---
title: "CodeBook.md"
output: html_document
---

Data Set Information: The experiments have been carried out with a group of 30 volunteers within an age bracket of 19-48 years. Each person performed six activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING) wearing a smartphone (Samsung Galaxy S II) on the waist. Using its embedded accelerometer and gyroscope, we captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz. The experiments have been video-recorded to label the data manually

Variables:
```{r}
Subject (30 volunteers)
Activity Type (six types)
Measurements columns (561)
```

Step 1
```{r, echo=FALSE}
Merged each training and test sets using rbind
```
Step 2
```{r, echo=FALSE}
Extract mean and standard deviation using grep
```
Step 3
```{r, echo=FALSE}
From activity_labels.txt file, get the descriptive names of the activity. Update data set 'Y' with the names
```
Step 4
```{r, echo=FALSE}
Column bind subject, activity names and actual data 'X'. This forms tidy data set
```
Step 5
```{r, echo=FALSE}
Using for-loop to get averages. Also use unique each subject data in the data set.
```


